Thesis Draft

### 2015-09-27 main.tex
My artwork steps
Former-commit-id: e225a9e56867b09d4de3dd644880c1f53142a1fb

Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
\end{abstract}
\keywords{trash, art, value creation}

@@

Trash moves, all the time. It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or compostable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill. Even in the landfill, it does not remain still. Monster "waste handling dozers" move rubbish around, compact it and press it against the soil. More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche. When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement. This is how trash moves. But\ldots who moves on trash? In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish. In Latin America, it is mostly people. People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks. In many of the garbage dumps around the world, scavenging becomes a steady job. \quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is. (through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
% >

@@

@@

%%
%%
\subsection{Their statements}

%%%
%%%
%%%
\section{My Artwork/Project}

@@

%%
%%
\subsection{Artistic tactics}
Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.

@@

%%
%%
\subsection{Trash as History/Memory}
Walter Benjamin's trash aesthetics and Adornos reflection. \cite{bullock2012trash}

%%
%%
\subsection{Trash Aesthetics}

>>>>

\textbf{Driving questions} Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again.

\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.

\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims. Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.  
\end{abstract}
\keywords{trash, art, value creation, transformation}

@@

Trash moves, all the time. It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill. Even in the landfill, it does not remain still. Monster "waste handling dozers" move rubbish around, compact it and press it against the soil. More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche. When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement. This is how trash moves. But\ldots who moves on trash? In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish. In Latin America, it is mostly people. People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks. In many of the garbage dumps around the world, scavenging becomes a steady job. \quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is. (through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
% >

@@

%%
%%
\subsection{Art and activism}

@@

%%
%%
\subsection{Artist statements}

%%%
%%%
%%%
\section{My Artwork/Project}
Here stages of my artwork are listed:
\begin{itemize}
\item \textbf{Memories.} As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember. One of these (First of them) is from my primary school teacher. When I was third class my teacher give us a homework to bring colorful paper to make something(whatever it is I don't remember). The day after we bring some colorful paper but she did not. Instead of this she bring paper cut out from packages that are colorful, shinny and qualify. And I remember clearly that she suggest that same for us. Do not throw out packages, look for the useful parts and keep them to use later. 
\item \textbf{Motivation.} I can not throw them away. When I throw them I became sad for them. I have to find something useful for it. Even if I can not find it, I can pass it to another person who can make use of it for own purposes. We are humans that can produce, transform items. One of most developed species in the earth that produce and use tools. There is a lot of effort to produce thrown away and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. 
\item \textbf{Collecting.} One of the most found trash in my habitat is paper. I work at METU Technopolis, live at 100. yil which is the nearest settlement to METU and study at Bilkent. People live there commonly use paper and needs paper. Paper is nearly everywhere. Reusing the paper is not limited with recycling of it. There is a another ways of it. When we recycle them actually we again send away them and use it as we all know. (industrial papers and notebooks.) There is no richness here. Same type of paper. Produced after a industrial process. I collected them from my friends (people that have communicate often). Sometimes I collect them from trash bins and roads. 
\item \textbf{Transforming.} I turned them to notebooks. Actually I use it for my self. And while I was using of it I am very proud of it. I am studying nearly more 20 twenty years and I have always need for notebooks and use them. It is some sort of passion for me notebooks. Because I always admire notebook beautifully design or uniquely designed. I collect them whenever I find and most of the time I only save them for later use. 
\end{itemize}

@@

%%
%%
\subsection{Why giving away?}
Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.

%%
%%
\subsection{Why in the public space?}
To reach more audience. Actually the audience is out of the art galleries. They are walking in the streets. Putting them to next to people is much more effective. It is not visible and nearly it is hided from society. It is dirty. Removed from the society. There is a effort to hide them away. However in this project it is again showed to the society. Because it is revisited and reclaimed.

%%
%%
\subsection{Artistic tactics}
Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.

\subsection{Why is it art?}
Uses artistic methods? Does it represent anything? The idea is transforming things. Anything can be transformed and re-contextualized again. The limitation is our imagination and approach. It has a claim. In can be analyzed and examined in the context of art. It is hard to say that something is art or not. However it can be examined in the context of art. There are artworks reject art galleries. There are artworks also reject commodities. It has purpose that. spread out the idea in different manner. Subverts peoples ideas.

The work aims to liberate the imagination and change the way people see the trash.

@@

%%
%%
\subsection{Trash as History/Memory}
% TODO From encylopedia
\cite{bullock2012trash}

%%
%%
\subsection{Trash Aesthetics}
Walter Benjamin's trash aesthetics and Adornos reflection.

%%%
%%%
%%%
\section{Sample Phrases}
